---
title: 'Lab 3: Data Wrangling on Soccer Tournament Data'
date: 'July 9, 2020'
output:
  html_document: default
  pdf_document: default
---
```{r setup, message = F, include=FALSE}
library(tidyverse)
```

Soccer tournament data wrangling
--------------------------
Read the dataset of football games.
```{r,message=F}
d <- read_csv("../data/results.csv")
```

1. Select variables `date`, `home_team` and `away_team`.
```{r}
d %>% dplyr::select(date,home_team,away_team)
```
2. Subset games with **Brazil** as the home team.
```{r}
d %>% filter(home_team=="Brazil")
```

3. Choose the games that Brazil won as the home team, and select variables `date`, `away_team` and `tournament`.
```{r}
d %>% filter(home_team=="Brazil",home_score>away_score) %>% dplyr::select(date)
```

4. Add the difference of goals, and an indicator variable called `goleada` for when the difference of goals is large,  and select what we did only for Brazil. **Hint: use `ifelse`**.
```{r}
d<-d %>% mutate(goleada=abs(home_score-away_score))
```

5. What was the largest difference in goals within these games?
```{r}
max(d$goleada)
```

6. The top 5 goleadas?
```{r}
head((d %>% arrange(desc(goleada)))$goleada,5)
```
7. Summary on goals scored by home teams, such as `mean` of `home_score` and `away_score`, `std`, using `group_by` and `summarise`
```{r}
d1<-d %>% group_by(home_team) %>% summarize(mean_home_score=mean(home_score),mean_away_score=mean(away_score))
d1
```

8. Proportion of victories of **Brazil** on different tournaments against each opponent, for instance, **Argentina**.
```{r}
d2<-d %>% filter((home_team=="Brazil"&away_team=="Argentina")|(home_team=="Argentina"&away_team=="Brazil")) %>%
  group_by(tournament) %>%
  mutate(Brazilwin=(home_team=="Brazil"&home_score>away_score)|(away_team=="Brazil"&away_score>home_score)) %>%
  summarize(Brazilwinrate=sum(Brazilwin)/length(Brazilwin))
d2
```



